学術論文

### 2022-02-10 articles.Rmd
update

- [35] Hasegawa, A., Somatori, K., Nishimura, H., Hattori, Y., & Kunisato, Y. (in press). Depression, rumination, and impulsive action: A latent variable approach to behavioral impulsivity. The Journal of Psychology.

>>>>

- [37] Hasegawa, A., Oura, S., Yamamoto, T., Kunisato, Y., Matsuda, Y., & Adachi, M. (in press) Causes and consequences of stress generation: Longitudinal associations of negative events, aggressive behaviors, rumination, and depressive symptoms. Current Psychology

- [36] Hasegawa, A., Somatori, K., Nishimura, H., Hattori, Y., & Kunisato, Y. (2021). Depression, rumination, and impulsive action: A latent variable approach to behavioral impulsivity. The Journal of Psychology. https://doi.org/10.1080/00223980.2021.1956871

- [35] Kashihara, J., Takebayashi, Y., Kunisato, Y., & Ito, M. (2021) Classifying patients with depressive and anxiety disorders according to symptom network structures: A Gaussian graphical mixture model-based clustering. PLoS ONE 16(9): e0256902. https://doi.org/10.1371/journal.pone.0256902
